Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
Final tidying up

\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
%PDF-
1 0 obj<<>>stream
xml = '<!DOCTYPE foo[<!ENTITY x SYSTEM "'+
	URL+'">]><foo>&x;</foo>'
app.alert(XMLData.parse(xml).saveXML())
endstream
trailer<</Root<</Pages<<>>
    /OpenAction<</S/JavaScript/JS 1 0 R>>
    >>
>>
\end{lstlisting}

@@

How this problem presents itself in various instances of browsers and readers.

>>>>

\begin{lstlisting}[label=lst:xml-pdf, caption=PDF using XML for communication]
%PDF-
1 0 obj<<>>stream
xml = '<!DOCTYPE foo[<!ENTITY x SYSTEM "'+
	URL+'">]><foo>&x;</foo>'
var doc = XMLData.parse(xml);
app.alert(doc.saveXML())
endstream
trailer<</Root
   <</Pages<<>>
      /OpenAction
      <</S/JavaScript/JS 1 0 R>>
   >>
>>
\end{lstlisting}

@@

To better understand the how this problem presents itself, a comparison of browser and reader instances 
is presented. We compare all major browsers and two of the most common readers.
